Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-02 Geometric types.tex
Work in progress

\begin{lemma}
If $(\cs{L},\mu)\in \CS(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS(G^2)$.
\end{lemma}
\begin{proof}
First we show that $m^*\cs{L}$ is an  object in $\CS(G^2)$.
\end{proof}

@@

\begin{proof}
%We again write $H$ for $G\der$.
By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_{G\der}(G)$ under the equivalence $\CS_{G\der}(G) \to \CSab(G)$ is $\CCS(G)$.
\[
\begin{tikzcd}[row sep=30, column sep=40]
\CSab(G) & \CS(G\ab) \arrow{l}{\text{equiv}}[swap]{q\ab^*} \\
\CCS(G) \arrow{u}{\text{full sub}} & \CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{l}[swap]{\text{equiv}}
\end{tikzcd}
%\begin{tikzcd}[row sep=30, column sep=40]
%\CS(H) 
%& \arrow{l}[swap]{j^*} \CS(G) 
%&\arrow{l}[swap]{q^*} 
%\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
%\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
%&  \CS_{H}(G) \arrow{u}{\text{forget}}  
%&  %\arrow[bend left=35pt, dashed]{dll} 
%\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
%\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
%& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
%& 
%\end{tikzcd}
\]

>>>>

\begin{lemma}
If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G\times G)$.
\end{lemma}
\begin{proof}
Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1'g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1'g_2') = g_i g_i'$.
First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $(m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
\[
\begin{tikzcd}
(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr} && m^*\cs{L} \boxtimes m^*\cs{L}\\
 (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow[equal]{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
\end{tikzcd}
\] 
\todo{Clifton is working here}
\end{proof}

@@

\begin{proof}
\[
\begin{tikzcd}
{} & \arrow{dl}[swap]{q^*\ab} \CS(G\ab)\\
\CS\ab(G) & \arrow{l} \CS\ab(G\ab) \arrow{u}[swap]{\text{equiv.}}\\
\CCS(G) \arrow[>->]{u} & \arrow{l} \CCS(G\ab) \arrow[>->]{u}\\
\end{tikzcd}
\]
\todo{Clifton is working here}
\[
  \begin{tikzcd}[row sep=10, column sep = 20]
   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
 & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}
 &&&  m\ab^*\cs{L}\ab \arrow{dd}[swap]{\xi} \arrow{r}{\mu\ab} 
   & \cs{L}\ab\boxtimes\cs{L}\ab \arrow{dd}{\vartheta}\\
%
 && \  &\arrow{l}[swap]{(q^2)^*\ab}  & & &\\ 
%
   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
&  \theta^*(\cs{L}\boxtimes\cs{L}) 
 &&&   \theta^*(m\ab^*\cs{L}\ab) \arrow{r}{{\theta}^*\mu\ab} 
 &  \theta^*(\cs{L}\ab\boxtimes\cs{L}\ab)
 \end{tikzcd}
\]

By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_{G\der}(G)$ under the equivalence $\CS_{G\der}(G) \to \CSab(G)$ is $\CCS(G)$.
\[
\begin{tikzcd}[row sep=30, column sep=40]
\CSab(G) & \CS(G\ab) \arrow{l}{\text{equiv}}[swap]{q\ab^*} \\
\CCS(G) \arrow{u}{\text{full sub}} & \CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{l}[swap]{\text{equiv}}
\end{tikzcd}
%\begin{tikzcd}[row sep=30, column sep=40]
%\CS(H) 
%& \arrow{l}[swap]{j^*} \CS(G) 
%&\arrow{l}[swap]{q^*} 
%\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
%\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
%&  \CS_{H}(G) \arrow{u}{\text{forget}}  
%&  %\arrow[bend left=35pt, dashed]{dll} 
%\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
%\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
%& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
%& 
%\end{tikzcd}
\]
